The impact of cosmic variance on constraining the mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z \sim 3$

### 2014-04-03 paper/ms.tex
observational constraints

Our method is based on the comparison of observations and mock
catalogs. We use two different kinds of statistics to perform the
comparison: (i) the distribution of the surface number density
across fields and (ii) the angular correlation function.

In the next subsections we describe in detail the four key
elements int our work-flow. First we present (in two sub-sections) the
observations we take as a benchmark. Second, we describe the main
characteristics of the N-body simulation and the halo catalogs we
use. Third, we recount the important parameters of the simplified
model that we use to populate the halo catalogs with LAEs. Finally, we
describe some of the statistical tests we adopt to compare
observations and mocks .

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1b.pdf}
\includegraphics[width=0.45\linewidth,angle=0]{Fig1.pdf}
\caption{ \label{fig:halos} Left panel. Cumulative distribution of LAE number
  densities in all the fields observed by \citet{Yamada2012}. The
  point with the highest surface density corresponds to the densest
  sub-field in the SSA22 field. Right panel. Surface density of dark 
  matter halos as a function of a minimum halo mass. Each line
  represents one of the $210$ volumes of dimensions $46\times 35\times
  41$ $h^{-3}$ Mpc$^{3}$ in the Bolshoi simulation. The horizontal
  gray band represents the range of surface densities observed for
  LAEs at $z=3.1$ as reported by \citet{Yamada2012} and the dashed
  line the observational results by \citet{Ouchi2008}.}
\end{center} 
\end{figure*}

The primary observational constraint we use in this paper is the LAE number
density information at $z=3.1$ obtained by the panoramic narrow-band
survey presented by \cite{Yamada2012} from a survey
conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera,
which has a field of view covering $34\times 27$ arc-min, corresponding to a
comoving scale of $46\times35$ Mpc $h^{-1}$ at $z=3.09$.  The narrow
band filter used in the survey is centered at $4977$ \AA~with  $77$ \AA~width,
corresponding to the redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the detection of the Lyman-$\alpha$ line
centered at $z=3.09$. The authors reported a total  $2161$  LAEs with
an observed equivalent width, in the observer frame, larger than $190$
\AA~over a total survey area of $2.42$ deg$^{2}$ that includes 12
sub-fields,  this corresponds to an average surface number density of
$0.24\pm 0.01$ arcmin$^{-2}$.

@@

\item The Subaru/{\it
  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South fields , with a
total of $0.58$ deg$^2$ and $386$ LAEs (3 sub-fields).

\item The Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
$196$ LAEs (1 sub-field), and

@@

There is abundant observational work done on LAEs at redshift $z=3.1$
\citep{Kudritzki2000,Matsuda2005,Gawiser2007,Nilsson2007,Ouchi2008}.
However, we decide to focus on the data from \cite{Yamada2012} because
it has the largest covered area with homogeneous instrumentation
conditions (telescope, narrow band filter), data reduction pipeline
and conditions to construct the LAE catalog. This ensures that the
number density variations among fields are \emph{not} due to different
observational conditions or criteria to construct the catalogs.

A secondary benchmark is the angular correlation function
(ACF). \cite{Yamada2012} does not report an ACF measurement for
  their fields. Instead we use the results by   \cite{Ouchi2008} who
  reported the ACF is over a region of $1$ deg$^2$ over the SXDS
  field.

There are some differences between \cite{Ouchi2008} observations
  and those by \cite{Yamada2012}. The details in the color selection,
  corresponding limiting luminosities and EW thresholds are different
  in these references. In the case of
  \cite{Ouchi2008} the number density is $0.099\pm0.005$ arcmin$^{-2}$, which
  is 50\% lower that the median value of $0.20$ arcmin$^{-2}$ for the
  the general fields in \cite{Yamada2012}. In spite of these
  differences \cite{Ouchi2008} provides the most similar conditions
  to \cite{Yamada2012}.

\subsubsection{The adequacy of including SSA22 as an observational benchmark}

The field SSA22 has been known to harbor a significant
  galaxy overdensity. \cite{Yamada2012} estimates that the densest
  sub-field is likely to be a rare density peak with $3-4\sigma$
  significance on the scale of $\sim 60$\hMpc.

All the other sub-fields in SSA22 are average. They have a similar
  number density as other blank fields. The left panel in Figure
  \ref{fig:halos} shows the integrated distribution of LAEs number
  density in all the fields reported in  \cite{Yamada2012}. It is
  evident that there is only one sub-field  that stands out as an
  outlier in the distribution, corresponding to  the densest field in
  SSA22. All the other fields form a continuous  distribution in
  number density.

Therefore, using the whole SSA22 region as a benchmark in the
  number density distribution does not impose any bias. However, on
  has to  keep in mind that is not plausible that the full number
  density distribution from a simulation will include a very dense
  field. For this reason we do not require the presence of a very
  dense field such as SSA22-1 to judge a mock distribution as
  successful. The statistical test we use o compare mock
  distributions against observations does not require such a perfect
  match.

@@

>>>>

Our method is based on the comparison of observations and mock
catalogs that take into account cosmic variance. Our benchmarks are the
distribution of the surface number density across fields and the
angular correlation function.

In the next subsections we describe in detail the four key
elements int our work-flow. First, we present the 
observations we take as a benchmark. Second, we describe the main
characteristics of the N-body simulation and the halo catalogs we
use. Third, we list the important parameters of the simplified
model that we use to populate the halo catalogs with LAEs. Finally, we
describe the statistical tests we adopt to compare observations and mocks.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\linewidth,angle=0]{Fig1b.pdf}
\caption{ \label{fig:number_density} Cumulative distribution of LAE number
  densities in all the fields observed by \citet{Yamada2012}. The
  point with the highest surface density corresponds to the densest
  sub-field in the SSA22 field.}
\end{center} 
\end{figure}

The first observational constraint we use in this paper is the LAE number
density information at $z=3.1$ obtained by \cite{Yamada2012} from a survey
conducted with the Subaru 8.2m telescope and the Subaru Prime Focus Camera.
The camera has a field of view covering $34\times 27$ arc-min,
corresponding approximately to a comoving scale of $46\times35$ Mpc
$h^{-1}$ at $z=3.09$.

The narrow band filter used in the survey is
centered at $4977$ \AA~with  $77$ \AA~width, corresponding to the
redshift range $z=3.062$-$3.125$ and $41$ \hMpc comoving scale for the
detection of the Lyman-$\alpha$ line centered at $z=3.09$. The authors
reported a total  $2161$  LAEs with an observed equivalent width, in
the observer frame, larger than $190$ \AA~over a total survey area of
$2.42$ deg$^{2}$ that includes 12 sub-fields,  this corresponds to an
average surface number density of $0.24\pm 0.01$ arcmin$^{-2}$.  The
distribution of the surface number densities is shown in Figure
\ref{fig:number_density}.

@@

\item The Subaru/{\it
  XMM-Newton} Deep Survey (SXDS)-North, -Center and -South fields, with a
total of $0.58$ deg$^2$ and $386$ LAEs (3 sub-fields).

\item The Subaru Deep Field (SDF) with $0.22$ deg$^2$ and
$196$ LAEs (1 sub-field).

@@

The surface number density distribution for these fields is shown in
Figure \ref{fig:number_density}.

There is abundant observational work done on LAEs at redshift $z=3.1$
\citep{Kudritzki2000,Matsuda2005,Gawiser2007,Nilsson2007,Ouchi2008}.
However, we use the data from \cite{Yamada2012} because
it has the largest covered area with homogeneous instrumentation
conditions (telescope, narrow band filter), data reduction pipeline
and conditions to construct the LAE catalog. This ensures that the
number density variations among fields are not due to different
observational conditions or criteria to construct the catalogs.

The second benchmark is the angular correlation function
(ACF). Unfortunately, \cite{Yamada2012} do  not report an ACF measurement for
their fields. Instead, we use the results by   \cite{Ouchi2008} who
reported the ACF is over a region of $1$ deg$^2$ over the SXDS
field.

There are some differences between \cite{Ouchi2008} observations
and those by \cite{Yamada2012}. The details in the color selection,
corresponding limiting luminosities and EW thresholds are different
in these references. In the case of
\cite{Ouchi2008} the number density is $0.099\pm0.005$ arcmin$^{-2}$, which
is 50\% lower that the median value of $0.20$ arcmin$^{-2}$ for the
the general fields in \cite{Yamada2012}. In spite of these
differences \cite{Ouchi2008} provides the most similar conditions
to the observations presented by \cite{Yamada2012}.

We note that the field SSA22-1 has been known to harbor a significant
galaxy overdensity. \cite{Yamada2012} estimates that the densest
sub-field is likely to be a rare density peak with $3-4\sigma$
significance on the scale of $\sim 60$\hMpc.  All the other sub-fields
in SSA22 are average with similar number density as other blank fields.

From Figure \ref{fig:number_density}  it is evident that there is only
one sub-field  that stands out as an outlier in the distribution,
corresponding to SSA22-1. All the other fields form a continous
distribution in number density. Therefore, using the whole SSA22
region as a benchmark in the number density distribution does not
impose any bias. The statistical test we use o compare mock
distributions against observations does not require a perfect match
with observations, i.e. the presence of a mock fields as dense as
SSA22-1 (which is very unlikely) is not required to consider that we
have a good match with observations.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.95\linewidth,angle=0]{Fig1.pdf}
\caption{ \label{fig:halos} Surface density of dark 
  matter halos as a function of a minimum halo mass. Each line
  represents one of the $210$ volumes of dimensions $46\times 35\times
  41$ $h^{-3}$ Mpc$^{3}$ in the Bolshoi simulation. The horizontal
  gray band represents the range of surface densities observed for
  LAEs at $z=3.1$ as reported by \citet{Yamada2012} and the dashed
  line the observational results by \citet{Ouchi2008}.}
\end{center} 
\end{figure}
